---
title: "Git Demo"
author: "Thomas Day"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pats Introduction

Pat Writes a great introduction with a great hook.

## Pat's contribution

Pat adds a great section to the document. It has great analysis and code.

```{r}
# Here is some of Pat's great code
pats_first_var <- c(1, 2, 3, 4)
pats_second_var <- c('a', 'b', 'c', 'd')

pats_df <- data.frame(var1 = pats_first_var, var2 = pats_second_var)

str(pats_df)
```

Some more of Pat's write up, transitioning to new code block.

```{r}
# Pat's new code block
table(pats_df)

mean(pats_df$var1)
```

You add some insight to Pat's work and pose another question.

```{r}
# Your great code
your_first_var <- c('i', 'ii', 'iii', 'iv')
your_second_var <- c('first', 'second', 'third', 'fourth')

your_df <- data.frame(var1 = your_first_var, var2 = your_second_var)

str(your_df)
```

You interpret your work and give discussion.

Pat concludes the section by discussing the code's output.

## You Conclusion

You conclude the report with great insight, tying things together and posing a few future question that could be researched. 
